Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-06-02 src/tex/ms.tex
Additional 2.1 edits

Aligned-spin, frequency domain waveform models (such as IMRPhenomD) can be written as a
combination of amplitude and phase functions ($A$ and $\phi$ respectively):
\begin{align}\label{eq:}
	h(f,\theta,\Lambda) = A(f,\theta,\Lambda)e^{-i\phi(f,\theta,\Lambda)}\,.
\end{align}
\te{Check minus sign}
Here $f$ is the frequnecy, $\theta$ are of intrinsic parameters of the binary, and $\Lambda$ is a set of additional
parameters which will be discussed below. 
The phase and amplitude functions are then split into three sections which represent the
inspiral, intermediate, and merger-ringdown (MR) parts of the waveform. 
During inspiral, $A$ and $\phi$ are known analytically from post-Newtonian (PN) theory;
PhenomD uses the TaylorF2 model \citep{boyle2007high} which is known up to 3.5PN order.
To model the intermediate and MR regions, IMRPhenomD (and all waveforms in the IMRPhenom family)
uses a series of parameterizations\footnote{
	The parameterizations for both the ampltude and phase functions can be found in \citep{khan2016frequency}.
} 
which depend purely on $\Lambda$ and can be calibrated to numerical relativity (NR) simulations.
The three sections are then \textit{stictched} together using step functions.
Importantly, the parameterizations are chosen such that they can be made $\mathcal{C}^1$ continuous at the
boundary between each section.

@@

At the time of construction this piece-wise fitting was necessary since
$\lambda$ has 209 components making the optimization computationally prohibitive.
Here, we recalibrate the $\lambda$ coefficients jointly. 
This is made possible by the use of gradient-based optimization algorithms which are
enabled by AD from \jax and {\ripple}.
% , gradients of IMRPhenomD can be easily obtained, thus
% allowing the use of gradient-based algorithms for us to recalibrate the model.

>>>>

Aligned-spin, frequency-domain waveform models (such as IMRPhenomD) can be written as a
combination of amplitude and phase functions ($A$ and $\phi$ respectively):
\begin{align}\label{eq:}
	h(f,\theta,\Lambda) = A(f,\theta,\Lambda)e^{-i\phi(f,\theta,\Lambda)}\,,
\end{align}
where $f$ is the frequnecy, $\theta$ are the intrinsic parameters of the binary, and $\Lambda$ is a set of additional
parameters which will be discussed below. 
The phase and amplitude functions are then split into three sections which represent the
inspiral, intermediate, and merger-ringdown (MR) parts of the waveform. 
During inspiral, $A$ and $\phi$ are known analytically from post-Newtonian (PN) theory;
IMRPhenomD uses the TaylorF2 model \citep{Buonanno:2009zt, Arun:2004hn} which is known up to 3.5PN order.
To model the intermediate and MR regions, IMRPhenomD (and all waveforms in the IMRPhenom family)
uses a series of parameterizations\footnote{
	The parameterizations for both the ampltude and phase functions can be found in \citep{khan2016frequency}.
} 
which depend purely on $\Lambda$ and can be calibrated to numerical relativity (NR) simulations.
The three sections are then \textit{stictched} together using step functions.
Importantly, the parameterizations are chosen such that they can be made $\mathcal{C}^1$ continuous at the
boundary between each section.

@@

At the time of construction this piece-wise approach was necessary since
$\lambda$ has 209 components, making the fitting to NR simulations computationally prohibitive.
Here, for the first time we recalibrate the $\lambda$ coefficients jointly. 
This is made possible by the use of gradient-based optimization algorithms,
enabled by AD from \jax and {\ripple}, which are significatnly moe efficient in high dimensions.
% , gradients of IMRPhenomD can be easily obtained, thus
% allowing the use of gradient-based algorithms for us to recalibrate the model.
